A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-02-22 doc/large_strain.tex
Adjust discussion on weak scaling

\changeJP{Extension of this study from the node level to the cluster level is beyond the scope of this work,
however we show preliminary weak scaling results that confirm that the matrix-free and multigrid frameworks implemented in the \texttt{deal.II} library can provide a competitive solution for that case as well.
Table \ref{tab:weak_3d} demonstrates a good weak scaling up to 1280 processes (64 nodes, the maximum we could request on the local HPC cluster) of the wall time for a single matrix-vector product and a single iteration in the CG solver for the 3D problem with quadratic basis.
}

>>>>

\changeJP{Extension of this study from the node level to the cluster level is beyond the scope of this work.
However, as a step in this direction we have performed a preliminary study of the weak scalability of the implementation.
Table \ref{tab:weak_3d} demonstrates a good weak scaling up to 1280 processes\footnote{%
This corresponds to 64 nodes, which is the maximum we could request on the RRZE Emmy HPC cluster.
} of the wall time per matrix-vector product and per iteration in the CG solver for the 3D problem with a tri-quadratic basis.
This confirms that the matrix-free and multigrid frameworks implemented in the \texttt{deal.II} library can provide a competitive solution for cluster-sized problems as well.
}
